---
title: "More Data Visualizations in R"
author: "YOUR NAME HERE"
date: ""
output: pdf_document
---

We will continue working with R so that our skills don't get too rusty. For this lab, we will continue with data visualiztion, reproducing plots from the R for Data Science, Data Visualization section: https://r4ds.had.co.nz/data-visualisation.html. You should follow the link to open the relevent webpage. We will be using some functions from the library tidyverse, which we have not seen in this class before this. Tidyverse automatically loads ggplot2, so we do not need a step for that.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# install.packages("tidyverse") # you shouldn't need this line unless you are working your personal computer and not on the server.
library(tidyverse)
```

## First steps

#### We will be working with the mpg dataframe found in ggplot2. It has been loaded automatically with the tidyverse package. Inspect the first 6 rows of the data frame below: 

```{r}

```

#### Create an appropriate plot to look at the relationship between hwy and displ.

```{r}

```

#### Complete the following exercises:

##### 1. Run ggplot(data = mpg). What do you see?

```{r}

```

##### 2. How many rows are in mpg? How many columns?

```{r}

```

##### 3. What does the drv variable describe? Read the help for ?mpg to find out.

```{r}

```

##### 4. Make a scatterplot of hwy vs cyl.

```{r}

```

##### 5. What happens if you make a scatterplot of class vs drv? Why is the plot not useful?

```{r}

```

## Aesthetic mappings

Read through this section in book before starting the exercises.

#### Exercises:

##### 1. What's wrong with this code? Why are the points not in blue? Fix it.

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))
```

##### 2. Which variables in mpg are categorical? Which variables are numerical? (Hint: type ?mpg to read the documentation for the dataset). How can you see this information when you run mpg?

```{r}

```

##### 3. Map a continuous variable to color, size, and shape. How do these aesthetics behave differently for categorical vs. continuous variables?

```{r}

```

##### 4. What happens if you map the same variable to multiple aesthetics?

```{r}

```

##### 5. What does the stroke aesthetic do? What shapes does it work with? (Hint: use `?geom_point`)

```{r}

```

##### 6. What happens if you map an aesthetic to something other than a variable name, like `aes(colour = displ < 5)`? Note, you'll also need to specify x and y.

```{r}

```

## Common problems

Read through the section on common problems. This will help you with debugging in the future.

If you have finished the above, and there is still class time left, please continue with the following:

## Facets

Read through the section on facets.

#### Exercises:

##### 1. What happens if you facet on a continuous variable?

```{r}

```

##### 2. What do the empty cells in plot with `facet_grid(drv ~ cyl)` mean? How do they relate to this plot?

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = drv, y = cyl))
```

##### 3. What plots does the following code make? What does . do?

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(drv ~ .)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(. ~ cyl)
```

##### 4. Take the first faceted plot in this section:

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2)
```

What are the advantages to using faceting instead of the colour aesthetic? What are the disadvantages? How might the balance change if you had a larger dataset?

##### 5. Read `?facet_wrap`. What does nrow do? What does ncol do? What other options control the layout of the individual panals? Why doesn't `facet_grid()` have nrow and ncol arguments?

```{r}

```

##### 6. When using `facet_grid()` you should usually put the variable with more unique levels in the columns. why?
